Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-24 paper/paper.tex
pass on intro

JavaScript (\js{}) is one of the most popular programming languages
today~\cite{redmonk-javascript,business-insider,stackify} with
penetration in various software development segments including, web, mobile,
and, more recently, the Internet of
Things~(IoT)~\cite{simply-technologies}. The interest of the community
for the language encourages constant improvements in its specification~\cite{ecmas262-spec}. It is natural to expect that such improvements
lead to sensible changes in engine implementations~\cite{kangax}. Even small
changes can have high practical impact. For example, in October 2014 a
new attribute added to Array objects resulted in the MS Outlook
Calendar web app failing under
Chrome~\cite{array-bug-chromium-issue4247,array-bug-discussion}.

Finding bugs in \js\ engines is an important problem given the range
of applications that could be affected with those
bugs. It\Comment{Finding bugs in \js\ engines} is also
challenging. For example, a test that passes in one engine could
legitimately fail in a different engine because of some undefined
behavior in the spec. These cases of undefined behavior can be
localized by searching for the string ``implementation-dependent'' in
the ES6 spec document~\cite{ecmas262-spec}. As another example, a test
may fail because the engine does not fully implement some feature. The
publicly-available Kangax compatibility table~\cite{kangax} relates
\js\ features with the engines that support them. To sum, it is often
non-trivial to assess if a test fails because of a bug or because of
some other reason making test automation more challenging. Developing
reliable engines is difficult because specifications are intentionally
incomplete as to enable flexibility during development and because
they evolve frequently.

%% WHAT WE DID
This paper reports on a study we ran to evaluate the importance of
diversity in finding bugs on JavaScript engines. We evaluated
effectiveness of two complementary diversity-aware testing
techniques. \emph{Test transplantation} leverages diversity of test
cases to find bugs. It evaluates the effects that running \js{} test
files from a given engine have in detecting bugs in other engines. The
intuition is that developers design test cases with different
objectives in mind. Replaying these tests, written for a given engine,
in a different engine may reveal unanticipated
problems. \emph{Cross-engine differential testing} evaluates the
ability of leveraging diversity of engine implementations to find
bugs. More precisely, this technique fuzzes existing test
inputs~\cite{fuzz-testing-history} and then compares the output
produced by different engines using a differential oracle. The
intuition is that \Fix{...}

@@

\emph{Related Ideas.}  It is worth noting that Differential
Testing~\cite{Brumley-etal-ss07} (DT) has been applied in a variety of
contexts to find
bugs~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17,Zhang:2017:ATD:3097368.3097448}.
It has shown to be specially practical in scenarios where the
observation of difference gives a strong signal of a real problem. For
example, Mozilla runs JS files\footnote{These files are created with
  the grammar-based fuzzer jsfunfuzz~\cite{jsfunfuzz}. Look for option
  ``compare\_jit'' from funfuzz.} against different configurations of
a given build of their \smonkey\ engine (\eg{}, trying to enable or
not eager JIT compilation). As the same engine is used in this
scenario, test outcomes are expected to be identical. The Mozilla team
uses this approach since 2002; they have been able to find over 270
bugs since then~\cite{jsfunfuzz-at-mozilla}, including security
bugs. Cross-engine differential testing, in contrast, has not been
very popularized. One possible reason is that it is still not
practical to fully automate the technique. In contrast to other
applications of differential testing, a number of legitimate reasons
exist, other than a bug, for a test execution to manifest discrepancy
(see Tables~\ref{fig:piecharts-transplantation} and
~\ref{tab:false-positives}).

@@

%% LIST OF CONTRIBUTIONS
This paper makes the following contributions.
\begin{itemize}
  \item We ran a comprehensive study to analyze the effectiveness of
    simple diversity-aware techniques to find bugs in highly-popular
    \js\ engines.

@@

  \item We offered insights on how to reduce cost of analyzing
    warnings reported by diversity-aware techniques and make the
    approach more practical.

  \item We made our testing infrastructure, results, and experimental
    scripts available to the public. (upon request for anonimity.)
\end{itemize}

@@

>>>>

% ,business-insider
JavaScript (\js{}) is one of the most popular programming languages
today~\cite{redmonk-javascript,stackify} with
penetration in various software development segments including, web, mobile,
and, more recently, the Internet of
Things~(IoT)~\cite{simply-technologies}. The interest of the community
for the language encourages constant improvements in its specification~\cite{ecmas262-spec}. It is natural to expect that such improvements
lead to sensible changes in engine implementations~\cite{kangax}. Even small
changes can have high practical impact. For example, in October 2014 a
new attribute added to Array objects resulted in the MS Outlook
Calendar web app, which is built in \js{}, failing under
Chrome~\cite{array-bug-chromium-issue4247,array-bug-discussion}.

Finding bugs in \js\ engines is an important problem given the range
of applications that could be affected with those bugs. It is also
challenging.  Specifications are intentionally incomplete as to enable
development flexibility. In addition, they evolve frequently to
accomodate the pressing demands from
developers~\cite{ecmas262-spec-repo}. An official conformance test
suites exist for \js~\cite{tc39-github}, but, naturally, many test
scenarios are not covered in the suite. In addition, we noticed that a
significant fraction (5 to 15\%) of the tests constantly fail on the
most popular engines, reflecting the struggle of developers in keeping
up with the pace of spec evolution (see Table~\ref{tab:test262}).

%% WHAT WE DID
This paper reports on a study we ran to evaluate the importance of
diversity in finding bugs on JavaScript engines. We evaluated
effectiveness of two complementary diversity-aware testing
techniques. \emph{Test transplantation} leverages diversity of test
cases to find bugs. It evaluates the effects that running \js{} test
files from a given engine have in detecting bugs in other engines. The
intuition is that developers design test cases with different
objectives in mind. Replaying these tests, written for a given engine,
in a different engine may reveal unanticipated
problems. \emph{Cross-engine differential testing} leverages diversity of engine implementations to find
bugs. More precisely, this technique fuzzes existing test
inputs~\cite{fuzz-testing-history} and then compares the output
produced by different engines using a differential oracle. The
intuition is that similar inputs to those already tested may reveal
problems. Our study measures the ability of these techniques in
finding bugs and the impact of false positives, which
can arise in both testing scenarios.

@@

\emph{Related Ideas.}  It is worth noting that Differential
Testing~\cite{Brumley-etal-ss07} (DT) has been applied in a variety of
contexts to find
bugs~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17,Zhang:2017:ATD:3097368.3097448}.
It has shown to be specially practical in scenarios where the
observation of difference gives a strong signal of a real problem. For
example, Mozilla runs JS files\footnote{These files are created with
  the grammar-based fuzzer jsfunfuzz~\cite{jsfunfuzz}. Look for option
  ``compare\_jit'' from funfuzz.} against different configurations of
a given build of their \smonkey\ engine (\eg{}, trying to enable or
not eager JIT compilation). A positive aspect of the aproach is that
it can be fully automated. As the same engine is used, the outcomes of
the test in both configurations are expected to be identical. The
Mozilla team uses this approach since 2002; they have been able to
find over 270 bugs since then~\cite{jsfunfuzz-at-mozilla}, including
security bugs. Cross-engine differential testing, in contrast, has not
been widely popularized. One possible reason is that it is still not
practical to fully automate the technique. In contrast to other
applications of differential testing, a number of legitimate reasons
exist, other than a bug, for a test execution to manifest discrepancy
(see Tables~\ref{fig:piecharts-transplantation} and
~\ref{tab:false-positives}). This paper evaluates the potential
benefits of diversity techniques, including DT. It provides data to
support or not the decision for automation of these techniques.

@@

%% LIST OF CONTRIBUTIONS
\emph{Contributions.}~This paper contributes the following:
\begin{itemize}
  \item We ran a comprehensive study to analyze the effectiveness of
    simple diversity-aware techniques to find bugs in highly-popular
    \js\ engines.

@@

  %% \item We offered insights on how to reduce cost of analyzing
  %%   warnings reported by diversity-aware techniques and make the
  %%   approach more practical.

  \item We made our testing infrastructure, results, and experimental
    scripts available to the public. (upon request for anonimity.)

\end{itemize}

@@

For example, a test that passes in one engine could
legitimately fail in a different engine because of some undefined
behavior in the spec. The most recent
\js\ specification~\cite{ecmas262-spec} documents several of these
cases, which can be traced looking for the string ``implementation-dependent''. As another example, a test
may fail because the engine does not fully implement some feature. The
publicly-available Kangax compatibility table~\cite{kangax} relates
\js\ features with the engines that support them. To sum, it is often
non-trivial to assess if a test fails because of a bug or because of
some other reason making test automation more challenging.
